### 2019-05-09 README.Rmd
use new link for taxize book at ropenscilabs now
docs fixes

The `taxize` tutorial is can be found at <https://ropensci.org/tutorials/taxize.html>

@@

	<td style="text-align:left;"><a href="http://www.eol.org/api/">link</a></td>
	<td style="text-align:left;"><a href="http://eol.org/users/register">link</a></td>

@@

	<td style="text-align:left;"><a href="http://www.catalogueoflife.org/colwebsite/content/web-services">link</a></td>

>>>>

The `taxize` tutorial is can be found at <https://ropensci.org/tutorials/taxize.html> and check out the taxize book <https://ropenscilabs.github.io/taxize-book/>

@@

	<td style="text-align:left;"><a href="https://eol.org/docs/what-is-eol/data-services">link</a></td>
	<td style="text-align:left;"><a href="https://eol.org/docs/what-is-eol/data-services">link</a></td>

@@

	<td style="text-align:left;"><a href="http://www.catalogueoflife.org/content/web-services">link</a></td>
